---
title: "IP5_JRR"
output: html_document
---

```{r setup, cache=TRUE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 Exploratory Data Analysis
---
**Author:** Jacob Redmon  
**Version:** 1.0  
**Semester:** Spring 2021  
**Summary:**  

The goal of this project is to use R and TidyVerse to clean up a data set and explore it by recreating IP4.

## I. Imports

```{r collapse=TRUE, message=FALSE}
library(datasets)
library(tidyverse)
library(psych)
library(corrplot)
```

## II. Data Set Description

```{r cache=TRUE}
df <- read.csv("movie_metadata.csv")
head(df)
str(df)
```

The columns are not in any particular, so I'll sort them in a more meaningful way.
```{r cache=TRUE}
col_order <- c('movie_title', 'title_year', 'country', 'language', 'budget', 'gross', 'imdb_score', 'duration', 'genres', 'plot_keywords', 'color', 'content_rating', 'aspect_ratio', 'facenumber_in_poster', 'num_critic_for_reviews', 'num_user_for_reviews', 'num_voted_users', 'director_name', 'actor_1_name', 'actor_2_name', 'actor_3_name', 'director_facebook_likes', 'actor_1_facebook_likes','actor_2_facebook_likes', 'actor_3_facebook_likes', 'cast_total_facebook_likes', 'movie_facebook_likes', 'movie_imdb_link')
dfa <- df[, col_order]
str(dfa)
```

```{r cache=TRUE}
describe(dfa)
```

There are many columns here that have missing data, I will remove all rows with missing data in any column and still be left with a sizeable data set. I will also reset the index since it is no longer continuous after dropping the missing data. The `aspect_ratio` column was messed up in the original data set as it should be a String but it is a float and now no longer makes sense, so I will drop the whole column.
```{r cache=TRUE}
dfa <- subset(dfa, select=-c(aspect_ratio))
dfa <- dfa[complete.cases(dfa), ]
row.names(dfa) <- NULL
nrow(dfa)
```

The `genres` column is too verbose, so I will create an additional column that takes just the first genre in the list, which is unfortunately in alphabetical order, so it may nor be the most accurate.
```{r cache=TRUE}
dfa$first_genre <- gsub('\\|.*','',dfa$genre)
head(dfa)
```

## III. Data Set Summary Statistics

Generate the Summary Statistics table.
```{r cache=TRUE}
dfb <- subset(dfa, select=-c(movie_title, country, language, genres, plot_keywords, color, content_rating, director_name, actor_1_name, actor_2_name, actor_3_name, movie_imdb_link, first_genre))
describe(dfb)
```

Generate the Proportions tables for the categorical variables.  
  
Function to calculate the proportion for categorical variables.
```{r cache=TRUE}
proportion <- function(x) {
    x <- x / 3873 * 100
}
```

Generate for proportion tables for categorical variables, the Reasonable Ones.
```{r cache=TRUE}
by_country <- dfa %>% count(country)
by_country <- within(by_country, prop <- proportion(by_country[2]))
by_country

by_language <- dfa %>% count(language)
by_language <- within(by_language, prop <- proportion(by_language[2]))
by_language

by_color <- dfa %>% count(color)
by_color <- within(by_color, prop <- proportion(by_color[2]))
by_color

by_content_rating <- dfa %>% count(content_rating)
by_content_rating <- within(by_content_rating, prop <- proportion(by_content_rating[2]))
by_content_rating

by_first_genre <- dfa %>% count(first_genre)
by_first_genre <- within(by_first_genre, prop <- proportion(by_first_genre[2]))
by_first_genre
```

Generate proportion tables for categorical variables, the Ones Who Shall Not Be Printed (because they're way too long).
```{r cache=TRUE, results='hide'}
by_plot_keywords <- dfa %>% count(plot_keywords)
by_plot_keywords <- within(by_plot_keywords, prop <- proportion(by_plot_keywords[2]))
by_plot_keywords

by_director_name <- dfa %>% count(director_name)
by_director_name <- within(by_director_name, prop <- proportion(by_director_name[2]))
by_director_name

by_actor_1_name <- dfa %>% count(actor_1_name)
by_actor_1_name <- within(by_actor_1_name, prop <- proportion(by_actor_1_name[2]))
by_actor_1_name

by_actor_2_name <- dfa %>% count(actor_2_name)
by_actor_2_name <- within(by_actor_2_name, prop <- proportion(by_actor_2_name[2]))
by_actor_2_name

by_actor_3_name <- dfa %>% count(actor_3_name)
by_actor_3_name <- within(by_actor_3_name, prop <- proportion(by_actor_3_name[2]))
by_actor_3_name
```

Generate a correlation matrix for all continuous variables
```{r cache=TRUE}
corr <- cor(dfb, use = "complete.obs")
corrplot(corr, type='full')
```

## IV. Data Set Graphical Exploration

### *A. Distributions*

```{r cache=TRUE}
hist(dfa$title_year)
hist(dfa$budget)
hist(dfa$gross)
hist(dfa$imdb_score)
hist(dfa$duration)
hist(dfa$facenumber_in_poster)
hist(dfa$num_critic_for_reviews)
hist(dfa$num_user_for_reviews)
hist(dfa$num_voted_users)
hist(dfa$director_facebook_likes)
hist(dfa$actor_1_facebook_likes)
hist(dfa$actor_2_facebook_likes)
hist(dfa$actor_3_facebook_likes)
hist(dfa$cast_total_facebook_likes)
hist(dfa$movie_facebook_likes)
```

### *B. Scatterplots / Pairwise Plots*

```{r cache=TRUE}
plot(dfa$duration, dfa$imdb_score, main="Duration vs. IMDB Score")
dfc <- subset(dfa, (budget<100000000))
plot(dfc$budget, dfc$gross, main="Budget vs. Gross where Budget < $100,000,000")
dfd <- subset(dfa, (budget<100000000))
plot(dfd$movie_facebook_likes, dfd$imdb_score, main="Movie Facebook Likes vs. IMDB Score where Budget > $100,000,000")
```

### *C. Barcharts*

```{r cache=TRUE}

```

### *D. Other Plots*

```{r cache=TRUE}
#pairplot(dfa)
```