---
title: "IP5_JRR"
output: html_document
---

```{r setup, cache=TRUE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 Exploratory Data Analysis
---
**Author:** Jacob Redmon  
**Version:** 1.0  
**Semester:** Spring 2021  
**Summary:**  

The goal of this project is to use R and TidyVerse to clean up a data set and explore it by recreating IP4.

## I. Imports

```{r cache=TRUE, collapse=TRUE, message=FALSE}
library(datasets)
library(tidyverse)
library(psych)
```

## II. Data Set Description

```{r cache=TRUE, results='hide'}
df <- read.csv("movie_metadata.csv")
head(df)
str(df)
```

The columns are not in any particular, so I'll sort them in a more meaningful way.

```{r cache=TRUE, results='hide'}
col_order <- c('movie_title',
    'title_year',
    'country',
    'language',
    'budget',
    'gross',
    'imdb_score',
    'duration',
    'genres',
    'plot_keywords',
    'color',
    'content_rating',
    'aspect_ratio',
    'facenumber_in_poster',
    'num_critic_for_reviews',
    'num_user_for_reviews',
    'num_voted_users',
    'director_name',
    'actor_1_name',
    'actor_2_name',
    'actor_3_name',
    'director_facebook_likes',
    'actor_1_facebook_likes',
    'actor_2_facebook_likes',
    'actor_3_facebook_likes',
    'cast_total_facebook_likes',
    'movie_facebook_likes',
    'movie_imdb_link')
dfa <- df[, col_order]
str(dfa)
```

```{r cache=TRUE, results='hide'}
describe(dfa)
```

There are many columns here that have missing data, I will remove all rows with missing data in any column and still be left with a sizeable data set. I will also reset the index since it is no longer continuous after dropping the missing data. The `aspect_ratio` column was messed up in the original data set as it should be a String but it is a float and now no longer makes sense, so I will drop the whole column.

```{r cache=TRUE, results='hide'}
dfa <- subset(dfa, select=-c(aspect_ratio))
dfa <- dfa[complete.cases(dfa), ]
row.names(dfa) <- NULL
nrow(dfa)
```

The `genres` column is too verbose, so I will create an additional column that takes just the first genre in the list, which is unfortunately in alphabetical order, so it may nor be the most accurate.

```{r cache=TRUE, results='hide'}
dfa$first_genre <- gsub('\\|.*','',dfa$genre)
head(dfa)
```

## III. Data Set Summary Statistics

Generate the Summary Statistics table.












```{r cache=TRUE}

```